Nonlinear methods to quantify Movement Variability in Human-Humanoid Interaction Activities

### 2021-06-29 docs/manuscript/main.tex
#15 minor changes to main.tex to build CITEX
#15 polishes acknowledgements CITEX

\section*{Acknowledgements}
This work was funded by the University of Birmingham and the Mexican National Council of Science and Technology as part of Miguel Xochicale's PhD degree.
I would like to thank to Dr. Dolores Columba Perez Flores and Prof. Martin J Russell for their helpful comments to polish the use of the language of mathematics and to Constantino Antonio Garcia Martinez et al. for developing the R package nonlinearTseries that help to accelerate the analysis of the nonlinear time series in this work.

>>>>

\section*{Acknowledgements}
This work was partially funded by both the University of Birmingham and the Mexican National Council of Science and Technology as part of Miguel Xochicale's PhD degree.      
I would like to thank to Dr. Dolores Columba Perez Flores and Prof. Martin J Russell for their helpful comments to polish the use of the language of Mathematics.    
Last but not least, thanks to Constantino Antonio Garcia Martinez et al. for developing the R package nonlinearTseries that help to accelerate the analysis of the nonlinear time series in this work.
